Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-05-24 awipev-CO2.Rmd
script for poster

# #plot for POSTER june 2019
# #plot of S/T
# poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
#   geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
#   labs(x = "Time", y="Temperature (°C)") +
#   scale_x_datetime(date_minor_breaks ="1 month")+
#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
#   scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity (PSU)"))
# print(poster_temp)
# 
# png("poster_sal_temp.png", width= 1100, height=600)
# par(mar=c(5, 4, 4, 6) + 0.1)
# 
# plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
# axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
# 
#     grid(lty=1)
# 
#    par(new = T)
# 
# plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
# axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
# mtext("Time",side=1,col="black",line=1.5, cex=1.8)
# legend("topleft", legend=c("Temperature (°C)", "Salinity (PSU)"),
#        col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
#   #grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
#    #  lwd = "months")
#      box()
#      dev.off()

@@

at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb, y= at, label = month))+
  geom_text( aes(color=factor(month))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity", y="Discrete TA", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
  theme_bw() + 
  theme(aspect.ratio=1,
        axis.text=element_text(size=15),
        axis.title.y= element_text(size =15),
        axis.title.x= element_text(size =15),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70))) 
  #print(at_s)

@@

# #plot for POSTER june 2019
# #plot of TA calculated from S + discrete
# p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
#   geom_point(col="blue", size=0.5 )+
#   geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
#   labs(title=  "Calculated TA from salinity (µmoles/kg)", x = "Time", y= "") +
#   scale_x_datetime(date_minor_breaks ="1 month")+
#   theme_bw() + theme(legend.position= c(0.7, 0.15), 
#                      legend.text=element_text(size=15),
#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 10, b = -20)),
#                      axis.text=element_text(size=15),
#                      axis.title.x= element_text(size =15),
#                      legend.title=element_blank())
# 
#   
# print(p_at_sal)
# ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")

@@

#plot for POSTER june 2019
#plot of pCO2
poster_pco2 <- ggplot( ) +
  geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros,col="blue"), col="blue",size=0.5 ) +
  geom_point(data=d_all, aes(x=datetime, y=pco2calc, fill="Calculated from AT/CT"), col="red" )+
  labs(x = "Time", y ="", title = expression(~italic(p)~CO[2]~"(µatm)")) +
  theme_bw() + theme(legend.position= c(0.59, 0.1),
                     legend.text=element_text(size=14),
                     plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
                     axis.text=element_text(size=15),
                     plot.margin = unit(c(0.5,1,1,1), "cm"),
                     axis.title.x= element_text(size =15),
                     legend.title=element_blank())
print(poster_pco2)
ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")

@@

# #plot for POSTER june 2019
# #plot of pH seafet
# poster_ph <- ggplot( ) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Discrete measurements"), col="red" )+
#   labs(x = "Time", y ="", title = expression(pH[T]~seaFET)) +
#   theme_bw() + theme(legend.position= c(0.8, 0.1), 
#                      legend.text=element_text(size=14),
#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
#                       axis.text=element_text(size=15),
#                       plot.margin = unit(c(1,1,1,1), "cm"),
#                       axis.title.x= element_text(size =15),
#                       legend.title=element_blank())
# 
# print(poster_ph)
# ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")
# 
# # RANGE of pH
# d_all<- d_all%>%
#   dplyr::mutate(year = year(datetime))
# range <- tbl_df(
#   d_all %>%
#   group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
#   summarize(pH_range = max(pHint_tot_sf) - min(pHint_tot_sf))
# )
# quant <- quantile(range$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
# 
# # Per month
# range_month <-
#   range %>%
#   group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
#   summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
# 
# size_point <- 0.4 # size of data points
# plot_range_sf <-  
#   ggplot(data=range, aes(x = as.factor(month), y = pH_range)) +
#   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
#   geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
#   labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +
#   Mytheme() +
#   theme(panel.grid.major.x = element_blank())
# print(plot_range_sf)
# ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")

@@

# #plot for POSTER june 2019
# #plot of pH durafet
# poster_dur <- ggplot( ) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Discrete measurements"), col="red" )+
#   labs(x = "Time", y= "", title = expression(pH[T]~durafet)) +
#   theme_bw() + theme(legend.position= c(0.7, 0.8), 
#                      legend.text=element_text(size=14),
#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
#                       axis.text=element_text(size=15),
#                       plot.margin = unit(c(1,1,1,1), "cm"),
#                       axis.title.x= element_text(size =15),
#                       legend.title=element_blank())
# 
# print(poster_dur)
# ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")
# 
# # RANGE of pH
# range_dur <- tbl_df(
#   d_all %>%
#   group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
#   summarize(pH_range = max(pH_durafet_corrected) - min(pH_durafet_corrected))
# )
# quant <- quantile(range_dur$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
# 
# # Per month
# range_month <-
#   range_dur %>%
#   group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
#   summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
# 
# size_point <- 0.4 # size of data points
# plot_range_dur <-  
#   ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
#   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
#   geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
#   labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
#   Mytheme() +
#   theme(panel.grid.major.x = element_blank())
# print(plot_range_dur)
# ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
```
The average offset between durafet and references (spectro) data is `r average_offset_dur` pH unit (sd = `r sd_offset_dur`, n = `r n_offset_dur`).

@@

###**FerryBox**
- **2019-04-14**: FB is working again. 
- **2019-04-13**: FB is stopped since 05:00am (the level switch stuck in the full position in the waste tank). 
- **2019-02-27**: FB is working again. 
- **2019-02-26**: FB is stopped because of a "leakage" issue. 
- **2019-01-17**: FB is stopped until 19th January 
- **2019-01-11**: FB is stopped until 12th Decmeber. 
- **2018-12-28**: FB is stopped until 31st Decmeber. 
- **2018-10-12**: FB is working again. 
- **2018-10-10**: FB is stopped after a seawater leakage. 
- **2018-10-08**: FB is working again. 
- **2018-10-05**: FB is stopped after a seawater leakage. 
- **2018-09-12**: FB is stopped. Problems inland could be the reason. The same day Marine make it working again.
- **2018-04-14**: FB is working again. They made an outlet "by-pass" tube to flush the seawater directly on the beach, not at 11 m.
- **2018-03-08**: Last data at 23:59. Frozen Ferrybox system (outlet tubings) in Svalbard, maybe due to a power failure over night in Kingsbay. UWO parameters (seaFET and SBE38 are still runing)
- **2017-05-24**: FerryBox was shut down due to many connexion issues...see Philipp's email 24/05/2017 18:17.
- **2017-03-20**: Philipp arrived in NYA to solve the problem.
- **2017-03-11**: Iceberg destroyed the power-pumps cables (Philipp's email on 2017-03-11 10:40). No more data for all parameters.
- **2017-01-31**: Beginning of the 14-days FB maintenance by Philipp and Uwe. Gaps in data could be present during this period.
- **2017-01-17**: Ferrybox stopped for unknown reasons from 2017-01-17 21:00 to 2017-01-19.
- **2016-09-24**: No data because of maintenance until the 28th. Except for TA wich has data available for this period.
- **2016-09-20**: Test in the Ferrybox with the seawater. Seawater was "sucked" (not pumped) from 7:40 to 10:00 by a vaccum system in order to test it. This system was installed if the pumps 1 and 2 broke during winter. This is a "plan C". This system is not automatic and we will be informed about its power up in case of emergency. As long as the water is not pumped with this system, we have to monitor the data because changements in gas partial pressure can occur.
- **2016-09-12**: No data because of maintenance until the 18th.
- **2016-09-10**: No data because of maintenance until the 11th.
- **2016-05-09**: data are back.
- **2016-05-04**: No data for all parameters because of electricity issues. 
- **2016-04-23**: FerryBox was shut down by AWI team for maintenance.
- **2016-02-23**: FerryBox was switched on by AWI team after maintenance.
- **2015-12-20**: FerryBox was shut down because of pump issues. Waiting for the maintenance in February.
- **2015-11-27**: The ferrybox was down from Nov. 18th until today Nov. 27th. (emails from P.Fischer 2015-11-24 23:09 and Station Leader AWIPEV 2015-11-27 12:57). Tubes frozen.

>>>>

# #plot for POSTER june 2019
# #plot of S/T
# poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
#   geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
#   labs(x = "Time", y="Temperature (°C)") +
#   scale_x_datetime(date_minor_breaks ="1 month")+
#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
#   scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity"))
# print(poster_temp)
# 
# png("figures/poster_sal_temp.png", width= 1100, height=600)
# par(mar=c(5, 4, 4, 6) + 0.1)
# 
# plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
# axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
# 
#     grid(lty=1)
# 
#    par(new = T)
# 
# plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
# axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
# mtext("",side=1,col="black",line=1.5, cex=1.8)
# legend("topleft", legend=c("Temperature (°C)", "Salinity"),
#        col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
#   #grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
#    #  lwd = "months")
#      box()
#      dev.off()

@@

at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb, y= at, label = month))+
  geom_text( aes(color=factor(month))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity", y="Discrete AT", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
  theme_bw() + 
  theme(aspect.ratio=1,
        axis.text=element_text(size=15),
        axis.title.y= element_text(size =15),
        axis.title.x= element_text(size =15),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70))) 
  #print(at_s)

@@

# #plot for POSTER june 2019
# #plot of TA calculated from S + discrete
# p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
#   geom_point(col="blue", size=0.5 )+
#   geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
#   labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
#   theme(legend.position= c(0.5, 0.93),
#                      legend.text=element_text(size=15),
#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
#                      axis.text=element_text(size=15),
#                      axis.title.x= element_text(size =15),
#                      legend.title=element_blank())
# 
# 
# print(p_at_sal)
# ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")

@@

#plot for POSTER june 2019
#plot of pCO2

#  add pCO2 atmospheric data from URL

# noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
# noaa <- noaa %>%
#   dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
#   unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
#   unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
#   unite("datetime", c("date", "time"), sep=" ")
#  
# noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
# noaa <- noaa %>%
#  dplyr::filter(datetime > "2015-07-01 00:00:00")
# 
# 
# poster_pco2 <- ggplot( ) +
#   geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros,col="blue"), col="blue",size=0.5 ) +
#   geom_point(data=d_all, aes(x=datetime, y=pco2calc), col="red" )+
#   geom_point() +geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value),size=0.5 ) +
#   scale_color_manual("",values=c("red", "blue", "black"), labels=c("pH spectro", "seaFET EXT ", "seaFET EXT corrected"))+
#   labs(x = "", y ="", title = expression(paste(italic(p),CO[2]," (µatm)"))) +
#   theme_bw() + theme(legend.position= c(0.59, 0.1),
#                      legend.text=element_text(size=14),
#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
#                      axis.text=element_text(size=15),
#                      plot.margin = unit(c(0.5,1,1,1), "cm"),
#                      axis.title.x= element_text(size =15),
#                      legend.title=element_blank())
# print(poster_pco2)
# ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")

@@

# #plot for POSTER june 2019
# #plot of pH seafet
# poster_ph <- ggplot( ) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Discrete measurements"), col="red" )+
#   labs(x = "", y ="", title = expression(pH[T]~seaFET)) +
#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
#   theme(legend.position= c(0.17, 0.8),
#                      legend.text=element_text(size=14),
#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
#                       axis.text=element_text(size=15),
#                       plot.margin = unit(c(1,1,1,1), "cm"),
#                       axis.title.x= element_text(size =15),
#                       legend.title=element_blank())
# 
# print(poster_ph)
# ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")

# # RANGE of pH
# d_all<- d_all%>%
#   dplyr::mutate(year = year(datetime))
# range <- tbl_df(
#   d_all %>%
#   group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
#   summarize(pH_range = max(pHint_tot_sf) - min(pHint_tot_sf))
# )
# quant <- quantile(range$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
# 
# # Per month
# range_month <-
#   range %>%
#   group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
#   summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
# 
# size_point <- 0.4 # size of data points
# plot_range_sf <-  
#   ggplot(data=range, aes(x = as.factor(month), y = pH_range)) +
#   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
#   geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
#   labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +
#   Mytheme() +
#   theme(panel.grid.major.x = element_blank())
# print(plot_range_sf)
# ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")

@@

# #plot for POSTER june 2019
# #plot of pH durafet
#  poster_dur <- ggplot( ) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Discrete measurements"), col="red" )+
#   labs(x = "", y= "", title = expression(pH[T]~durafet)) +
#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
#    theme(legend.position= c(0.17, 0.8),
#                      legend.text=element_text(size=14),
#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
#                       axis.text=element_text(size=15),
#                       plot.margin = unit(c(1,1,1,1), "cm"),
#                       axis.title.x= element_text(size =15),
#                       legend.title=element_blank())
# 
# print(poster_dur)
# ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")
# 
# # RANGE of pH
# range_dur <- tbl_df(
#   d_all %>%
#   group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
#   summarize(pH_range = max(pH_durafet_corrected) - min(pH_durafet_corrected))
# )
# quant <- quantile(range_dur$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
# 
# # Per month
# range_month <-
#   range_dur %>%
#   group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
#   summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
# 
# size_point <- 0.4 # size of data points
# plot_range_dur <-  
#   ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
#   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
#   geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
#   labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
#   Mytheme() +
#   theme(panel.grid.major.x = element_blank())
# print(plot_range_dur)
# ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
```
The average offset between durafet and references (spectro) data is `r average_offset_dur` pH unit (sd = `r sd_offset_dur`, n = `r n_offset_dur`).

@@

###**FerryBox**
- **2019-05-22**: FB is stopped because of several problems. Philipp and Marine are working on it.
- **2019-05-21**: FB is unstable. 
- **2019-04-14**: FB is working again. 
- **2019-04-13**: FB is stopped since 05:00am (the level switch stuck in the full position in the waste tank). 
- **2019-02-27**: FB is working again. 
- **2019-02-26**: FB is stopped because of a "leakage" issue. 
- **2019-01-17**: FB is stopped until 19th January 
- **2019-01-11**: FB is stopped until 12th Decmeber. 
- **2018-12-28**: FB is stopped until 31st Decmeber. 
- **2018-10-12**: FB is working again. 
- **2018-10-10**: FB is stopped after a seawater leakage. 
- **2018-10-08**: FB is working again. 
- **2018-10-05**: FB is stopped after a seawater leakage. 
- **2018-09-12**: FB is stopped. Problems inland could be the reason. The same day Marine make it working again.
- **2018-04-14**: FB is working again. They made an outlet "by-pass" tube to flush the seawater directly on the beach, not at 11 m.
- **2018-03-08**: Last data at 23:59. Frozen Ferrybox system (outlet tubings) in Svalbard, maybe due to a power failure over night in Kingsbay. UWO parameters (seaFET and SBE38 are still runing)
- **2017-05-24**: FerryBox was shut down due to many connexion issues...see Philipp's email 24/05/2017 18:17.
- **2017-03-20**: Philipp arrived in NYA to solve the problem.
- **2017-03-11**: Iceberg destroyed the power-pumps cables (Philipp's email on 2017-03-11 10:40). No more data for all parameters.
- **2017-01-31**: Beginning of the 14-days FB maintenance by Philipp and Uwe. Gaps in data could be present during this period.
- **2017-01-17**: Ferrybox stopped for unknown reasons from 2017-01-17 21:00 to 2017-01-19.
- **2016-09-24**: No data because of maintenance until the 28th. Except for TA wich has data available for this period.
- **2016-09-20**: Test in the Ferrybox with the seawater. Seawater was "sucked" (not pumped) from 7:40 to 10:00 by a vaccum system in order to test it. This system was installed if the pumps 1 and 2 broke during winter. This is a "plan C". This system is not automatic and we will be informed about its power up in case of emergency. As long as the water is not pumped with this system, we have to monitor the data because changements in gas partial pressure can occur.
- **2016-09-12**: No data because of maintenance until the 18th.
- **2016-09-10**: No data because of maintenance until the 11th.
- **2016-05-09**: data are back.
- **2016-05-04**: No data for all parameters because of electricity issues. 
- **2016-04-23**: FerryBox was shut down by AWI team for maintenance.
- **2016-02-23**: FerryBox was switched on by AWI team after maintenance.
- **2015-12-20**: FerryBox was shut down because of pump issues. Waiting for the maintenance in February.
- **2015-11-27**: The ferrybox was down from Nov. 18th until today Nov. 27th. (emails from P.Fischer 2015-11-24 23:09 and Station Leader AWIPEV 2015-11-27 12:57). Tubes frozen.
